QRF Covariate Selection

### 2020-01-25 analysis/R_scripts/fit_qrf_model.Rmd
added code to read in data about CHaMP frame from csv, but then save as .rds, so that it's smaller and can be pushed to GitHub.

# read in data from the CHaMP frame
champ_frame_df = read_csv('../data/derived_data/champ_frame_data.csv') %>%
  mutate(Target2014 = ifelse(is.na(AStrat2014), 'Non-Target', Target2014)) %>%
  mutate(AStrat2014 = ifelse(AStrat2014 == 'Entiat IMW', paste('EntiatIMW', GeoRchIMW, sep = '_'), AStrat2014)) %>%
  filter(Target2014 == 'Target') %>%
  rename(Watershed = CHaMPshed)

>>>>

# read in data from the CHaMP frame

# read it in from .csv once, then save as .rds object (smaller in size)
# champ_frame_df = read_csv('../data/derived_data/champ_frame_data.csv') %>%
#   mutate(Target2014 = ifelse(is.na(AStrat2014), 'Non-Target', Target2014)) %>%
#   mutate(AStrat2014 = ifelse(AStrat2014 == 'Entiat IMW', paste('EntiatIMW', GeoRchIMW, sep = '_'), AStrat2014)) %>%
#   filter(Target2014 == 'Target') %>%
#   rename(Watershed = CHaMPshed)
# 
# write_rds(champ_frame_df,
#           "../data/derived_data/champ_frame_data.rds")

champ_frame_df = read_rds("../data/derived_data/champ_frame_data.rds")
